### 2011-11-22 doc/theses/vitasek/appendix-c-trace.tex
Thesis: merging Kesy.

The second section states the input file along with its size and graph representation (Section \ref{section-experiments-data}). Alpha and beta parameters for this instance belong here too.

@@

After the last improvement phase, the reason why the metaheuristic terminated is stated. Possible causes are exceeding the maximum time available, maximum iterations or reaching the known optimum for this file and alpha / beta settings.
\\

>>>>

The second section states the input file along with its size and graph representation (Section \ref{section-experiments-data}). The $\alpha$ and $\beta$ parameters for this instance belong here, too.

@@

After the last improvement phase, the reason why the metaheuristic terminated is stated. Possible causes are exceeding the maximum time available, maximum iterations or reaching the known optimum for this file and $\alpha$ / $\beta$ settings.
\\

### 2011-11-22 doc/theses/vitasek/chapter-6-conclusion.tex
Thesis: merging Kesy.

The wisdom found in the experiments in this work might be the following. While it is important to be able to write a heuristic algorithm tailored to the specific problem being solved, such as the authors of \cite{fidax} did, it should be noted that sometimes it is better to solve a more generalized problem. In~this case the transformation to MIP formulation and using a dedicated solver proved to~produce better results in shorter time.

>>>>

The wisdom found in the experiments in this work might be the following. While it is important to be able to write a heuristic algorithm tailored to the specific problem being solved, such as the authors of \cite{fidax} did, it should be noted that sometimes it is better to solve a more general problem. In~this case the transformation to MIP formulation and using a dedicated solver proved to~produce better results in shorter time.
